### 2017-11-22 manuscript.rmd
fixed path to folder figures_for_AI and added par(ask=F) to avoid Hit Return <>

```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
pdf("density_sex_sim")
densityMap(sex_sim)
dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
pdf("palpons_sim")
densityMap(palpons_sim)
dev.off()
```

@@

pdf("trimmed_violinVars.pdf")
ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()
dev.off()
```

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
pdf("overview_ggheatmap_chars.pdf")
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
dev.off()
```

>>>>

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
pdf("figures_for_AI/density_sex_sim.pdf")
densityMap(sex_sim)
dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
pdf("figures_for_AI/palpons_sim.pdf")
densityMap(palpons_sim)
dev.off()
```

@@

pdf("figures_for_AI/trimmed_violinVars.pdf")
ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()
dev.off()
```

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
pdf("figures_for_AI/overview_ggheatmap_chars.pdf")
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
dev.off()
```
